A Machine Learning Approach to Kinematic Synthesis of Defect-Free Planar Four-Bar Linkages

### 2018-07-04 rebuttal/rebuttal.tex

\documentclass{article}
\usepackage{graphicx}
\title{Rebuttal}
\author{Shrinath Deshpande, Anurag Purwar}

\begin{document}
\maketitle
We are grateful to all of the reviewers, who took out their valuable time to review our paper. This work would be incomplete without the reviewers' inputs.
The reviewers' comments are given in \emph{italicized}, whereas our answers are in normal text.

\section{Reviewer 1}
%The authors propose applying machine learning techniques to solving planar four-bar linkage problems. The authors claim gaps exist in existing methods that do not account for circuit and branch defects in the synthesis process.
%Significant technical deficiencies and several editorial issues exist in the submitted manuscript. Therefore, this reviewer must recommend a reject and encourage the authors to make major revisions before the manuscript could be acceptable for publication.
\begin{itemize}
  \item \emph{
Overall, the paper lacks a clear motivation for why the described method is required.
The authors highlight several gaps in existing methods identified by the literature.
However, the authors do not explain how those defects affect current practice or why a new method is necessary.
While gaps may exist in current methods, are those gaps significant enough to not produce accurate results? If so, why? The introduction of the manuscript reads as a background knowledge section.
This reviewer recommends the authors include a new introduction that strongly motivates their work described in the manuscript and rename the current introduction.
Example questions for identifying a motivation are: what stakeholders benefit from the authors' contributions? What are the expected benefits and/or impacts of the novel contributions? To what type of real, practical problems does the method apply?
Overall, the paper lacks a clear motivation for why the described method is required.
Absent a strong motivation, the manuscript reads as if the authors pursued a machine-learning problem for the sake of machine learning. This reviewer finds little value in answering these types of research questions.
Manuscript lacks a clear motivation linked to the practitioner.
The research objective, methods, and approach are not clear.
}

Thank you for pointing out an important point.
We have rewritten the introduction section to clearly explain motivation and overview of the approach.
The motivation subsection clearly explains the significance of the gaps in current practices.
We summarize the motivation as follows,

The classical mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are categorized as the path, motion and function generation.
Path generation task aims to synthesize a mechanism which can guide a point along a prescribed path.
On the other hand, the objective of motion generation task is to synthesize a mechanism which can guide a rigid body along a prescribed motion.
The prescribed path is a time sequence of positions, whereas the prescribed motion is a time sequence of positions and orientations.

The majority of mechanism synthesis methods are based on the precision point approach.
This approach is a clever approximation trick to solve the synthesis tasks, where the task is discretized into precision points.
These points instead of the actual task, are treated as interpolation or approximation task for mechanism synthesis.
However, this way of formulation loses important information about the actual continuous task and can lead to solutions with the order, circuit and branch defects.
The defect in a mechanism renders itself useless for its intended application.

\begin{figure}
\centering
\includegraphics[width=200pt]{fig_circuit_defect.eps}
  \caption{The mechanism synthesis problem for the prescribed motion.
  The four-bar mechanism obtained using the precision position approach suffers from circuit defect, as no coupler circuit passes through all precision positions.}
\label{circuit_defect}
\end{figure}

Figure~\ref{circuit_defect} shows the prescribed motion and its discretized precision positions.
In the case of motion generation problem, a four-bar can go through at most five precision positions and it is called as classical Burmester~\cite{Burmester86} problem.
For this type of problem, only finite solutions exist and in this case only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
Although it can be seen that coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
A circuit represents an assembly mode in which the mechanism is put together.
This phenomenon is called circuit defect in the linkage, which makes the linkage useless for the prescribed task.
Even if the defect-free solution is found, the coupler motion in-between the precision points may go through undesired position and orientation.
This happens because the method discards the functional aspect of continuous motion and turns it into a vacuous interpolation problem.
This tells us that just finding a defect-free linkage with respect to the precision positions is not enough to qualify as a useful mechanism.

To capture the complete prescribed task, we represent it as a continuous parametric curve.
The objective is to find a linkage, that has a coupler motion or path compatible with the task.
Next step is to conduct a search in the space of linkage parameters to find linkages with coupler motions compatible with the prescribed task.
Although global search methods can be applied for finding solutions, we employ an efficiently clustered database and Powell's local search method to come up with a variety of different solutions.
We exploit machine learning to maximize the diversity, and for efficient storage of the linkage database.
The outcomes of this approach are a large number of diverse concept solutions.
The importance of diverse concept generation is mentioned in motivation subsection by following lines,
``Thus, the synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements."
\\

  \item \emph{
Further, most of the citations in the manuscript, not including the authors' previous work, are over 10 years old.
}

Thanks, we have added recent citations reporting the work in the area of mechanism synthesis and machine learning applications to mechanisms.
\\

@@

  \item \emph{
Instead, the authors should motivate their work with important use cases that address necessary research questions for an identified stakeholder. Tell the reader why this work is important? The authors claim the current approaches are useless for practical applications. What are the practical applications and what are their requirements? The authors do include two use cases, but their practical relevance is not discussed.
}

Thank you for your comments.
We have added the example shown in the Fig.~\ref{circuit_defect} to the motivation section, which clearly explains the limitations of current practices.
We have used the same example in the example section to clearly juxtapose our results against results of precision point approach.
\\

@@

  \item \emph{
 The reason for employing machine learning techniques is artificially explained in one sentence at the end of Section 3.3. Expand the reason for employing machine learning.
}

We have expanded the reason for employing machine learning techniques in the subsection titled 'Dimensionality Reduction using Auto-Encoders' as follows,

``In order to have efficient query operations, we perform Hierarchical Clustering; a method that summarizes and creates a hierarchy in the database.
Clustering in higher dimensions suffers from \emph{Curse of Dimensionality}\cite{marimont1979}, thus we first perform dimensionality reduction using Auto-encoder Neural Networks.
Auto-encoder is a powerful mapping model, which learns to encode the input data in very compact representation and can reconstruct the input with minimal error; performing much better than Principal Component Analysis\cite{hinton2006}.
This nonlinear mapping by auto-encoder can greatly improve the representation of data for clustering~\cite{song2013}."

In addition to that, we have added following lines to explain the motivation behind using clustering,
``We use machine learning techniques such as clustering and data-compression using auto-encoder neural networks to come up with good initial guesses for local optimization.
First, We cluster the database using hierarchical clustering algorithm.
Then, we find representative data point in each cluster called cluster center and form their set.
This set of cluster centers represent a diverse group of linkages.
When a query is raised in the database, the first step is to search for neighbors in the set of cluster centers.
This often yields a diverse set of neighbors and is used as a set of initial guesses for local optimization.
"
\\

  \item \emph{
  In Fig. 1 (overview), should an arrow return from ``Local Optimizer" to ``Accurate?" or is the assumption that all outputs from the ``Local Optimizer" are accurate?
}

Thank you for mentioning that.
We have fixed it.
\\

@@

  \item \emph{
The values used in the sensitivity analysis are not justified. How did the authors choose the values?
}

Thank you for the comment. We have added following line,
``The link ratios are chosen such that, small changes in some parameters lead to a topological change in the coupler curve."
\\

@@

  \item \emph{
The quality of research methods cannot be assessed.
}

We have employed already proven techniques such as b-spline interpolation, hierarchical clustering, data compression using auto-encoders, Powell's local search.
We have formulated the signatures of coupler path and motion, based on proven 2D curve matching technique by Cui et al.\cite{cui2009}.
We have presented the validation of the partial matching algorithms using examples in section 4.
Finally, we present two case studies, where we obtain the diverse set of useful linkage solutions for path and motion generation problem.
\\

@@

  \item \emph{
The conclusion is too short. It lacks a critical discussion of the research. The authors should critically assess the proposed approach.
}

Thanks for the important feedback, we have modified the conclusion by adding critical assessment of the approach as follows,
`` The problem formulation is invariant with respect to translation, orientation, and scaling.
Hence, constraints like geometric restrictions on pivots have to be addressed after finding feasible solutions for the task.
The approach is general enough to be extended to higher order linkage systems for which there are even fewer methods available for synthesizing defect-free solutions.
However, the database size increases exponentially with the number of links in the mechanisms.
As an example, a Watt type six-bar database needs to be roughly 400 times larger than four-bar database.

A potential solution to this problem could be to use learning based methods, where the pattern is learned instead of storing all of the information.
Overall, the method provides a holistic approach towards the prescribed path and motion synthesis and encourages artificial intelligence techniques to make an impact.
"

  \item \emph{
 Review the usage of ``that" versus ``which". There are some instances where the usage should be reversed.
 \\
 Several instances exist throughout the manuscript where nouns could benefit from having a ``the" put in from of them. For example, the first sentence of Section 5.1 reads as, ``Each data point in the database consists of discrete..." Instead, the sentence should read as, ``Each data point in [the] database consists of discrete..."
 Check usage of hyphens. Inconsistent usage exists in the manuscript.
 }

@@

  \item \emph{
$5.$ In Figure 15, $X$ and $\tilde{X}$ mismatch the input and output vectors shown in the diagram.
}

Figure 15 shows $X$ as the input and $\tilde{X}$ as the output of auto-encoder network, which matches with the description.
The query regarding the mismatch is not clear to us.
Could you please elaborate on the query?
\\

  \item \emph{
$7.$ In section 5.1, it is argued that Euclidean distance is used as the distance metric in latent space for
computational efficiency, whereas in section 6.1, $(1 − Cn)$ is mentioned as the distance
metric. Please clarify.
}

Thanks for the feedback. We have made changes in the text to clarify which metric is used at what point.
In section 5.1, we added following lines, ``The distance metric used for clustering is the Euclidean distance in the latent space.
Although the more accurate distance metric is distance function discussed in sec 3, it is very expensive to calculate it for the entire database.
Signatures with ${O}(m)$ points take ${O}(m\log{}m)$ time for each comparison and there are ${O}(N^2)$ number of comparisons to be made for the database of $N$ points.

Now, when the user raises a query, we use the distance function from sec.3 for finding $k$ nearest neighbors among $1500$ cluster centers.
If a cluster center is not sufficiently close, we descend into its corresponding cluster to find the closest data point.
The distance metric for finding neighbors among cluster centers is $1-Cn_{max}$ in Eq. 5.  "
\\

@@

  \item \emph{
$8.$ It is unclear how local optimization is performed after finding the nearest cluster centers. Is the
search performed in each cluster independently? Are multiple paths/motions in the database
combined with partial matching? Please elaborate.
}

Thanks for the comments.
We use the cluster centers as independent initial guesses and do a local search on each initial guess independently.
We have added following lines in section 5 to clarify that.

``When a query is raised in the database, the first step is to search for neighbors in the set of cluster centers.
This often yields a diverse set of neighbors, and is used as a set of independent initial guesses for local optimization."
\\

@@

  \item \emph{
$9.$ Please comment on how this approach can be extended to handle process specific constraints?
For example, the pivots should lie above ground in show-shoveling case study (6.2).
}

Thank you for mentioning that. We have added following lines in the conclusion.
``The partial matching metric although more accurate, but is expensive in terms of computation cost.
Thus, we use Euclidean metric in the latent space of compressed data for hierarchical clustering.
The formulation is invariant with respect to translation, orientation, and scaling.
Hence, constraints like geometric restrictions on pivots, have to be addressed after finding feasible solutions for the task."

### 2018-07-04 idetc2018_journal.tex
Comma fixes, Rebuttal fixes and some fixes in paper

The classical mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are categorized as the path, motion and function generation.
Path generation task aims to synthesize a mechanism, which can guide a point along a prescribed path.
On the other hand, the objective of motion generation task is to synthesize a mechanism, which can guide a rigid body along a prescribed motion\footnote{motion is the combination of position and orientation.}.
For an exhaustive reference, see books from McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt~\cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
Various approaches have been proposed in the literature with aim of finding acceptable solutions for path and motion generation problem.
In the majority of the methods, the first step is choosing a mechanism type and then calculating the design parameters of chosen mechanism type.
The prior step is called Type Synthesis, and the later step is Dimension Synthesis.
This paper presents an approach to Dimension Synthesis of planar four-bar linkages, but the approach is general enough to be applied on any planar linkage.

\subsection{Motivation}
The majority of mechanism synthesis methods are based on the precision point approach.
This approach is a clever approximation trick to solve the abovementioned tasks, where the task is discretized into precision points.
These points, instead of the actual task, are now treated as interpolation or approximation task for mechanism synthesis.
However, this way of formulation loses important information about the actual continuous task and can lead to solutions with the order, circuit and branch defects.
The defect in a mechanism renders itself useless for its intended application.
The defects in the single degree of freedom mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.

Let's see an example of this in a motion generation task.
The objective is to synthesize a four-bar mechanism that can perform the prescribed motion.
Figure~\ref{circuit_defect} shows the prescribed motion and its discretized precision positions.
In the case of motion generation problem, a four-bar can go through at most five precision positions, and it is called as classical Burmester~\cite{Burmester86} problem.
For this type of problem, only finite solutions exist and in this case, only one solution is obtained as shown in Fig.~\ref{circuit_defect}.
It can be seen that, although coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
A circuit represents an assembly mode in which the mechanism is put together.
This phenomenon is called circuit defect in the linkage, which makes the linkage useless for the prescribed task.
To deal with it, a naive approach is to tweak precision positions in a brute-force way within the tolerance until a solution is found.
Even if the defect-free solution is found, the coupler motion in-between the precision points may not have the desired properties.
This happens because the method discards the functional aspect of continuous motion and turns it into a vacuous interpolation problem.
This tells us that just finding a defect-free linkage with respect to the precision positions, is not enough to qualify as a useful mechanism.

Thus, we present a perceptive way of synthesizing defect free linkages for motion and path generation problems.
%As a guiding direction to advance state of the art, we propose following criteria for an effective mechanism synthesis method,
%  \item \textbf{Data Driven}: The method should evolve by learning from its previous experiences, including providing quicker solutions for problems similar to previously solved problems.
%\end{enumerate}
To capture the complete prescribed task, we represent it as a continuous parametric curve.
The objective is to find a linkage, that has a coupler motion or path compatible with the task.
We developed the compatibility measure in a way that is invariant to similarity transformations.
Next step is to conduct a search in the space of linkage parameters to find linkages with coupler motions compatible with the prescribed task.
Although global search methods can be applied for finding solutions, we employ an efficiently clustered database and Powell's local search method to come up with a variety of different solutions.
The motivation behind using clustered database is rooted in the broader objective of machine design.
Mechanism synthesis is a part of the conceptual design phase, which is one of the earliest stages of product design cycle of a machine.
Thus, the synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements.
The method only deals with the coupler curves and is indifferent to the linkage type.
Thus, it is readily scalable to any type of planar linkage.
In section~\ref{subsec_motiongen}, we present the obtained solutions for the prescribed motion presented in Fig.~\ref{circuit_defect}.

\subsection{Literature Survey}
% Global search methods
Instead of brute-force search within tolerance regions, some approaches apply separate constraints to take care of the defects and form an optimization problem of Non-Differentiable objective function.
It can be solved by metaheuristic algorithms like Differential-evolution(DE), Particle Swarm Optimization (PSO), Cuckoo Search (CS).
Cabrera et al.\cite{Cabrera2002} used Genetic Algorithm as the tool for optimization in mechanism synthesis.
Sardashti et al.\cite{sardashti2013} used PSO towards the defect-free synthesis of four-bar linkage with joint clearance for path generation problem.
Ebrahimi and Payvandy\cite{Ebrahimi2015} presented an application of Imperialist Competitive Algorithm (ICA) for synthesizing path generating four-bars having desired workspace limits.
Bulatovic\cite{Bulatovic2013} used Cuckoo Search for solving the problem of optimum synthesis of a six-bar double dwell linkage.
The above methods can produce many defect-free solutions and are scalable to any type of linkages.
However, these methods tend to be slow and inefficient, as they start from scratch for every instance, and with no guarantee of converging to an acceptable solution.

Path synthesis methods based on Fourier analysis do take the continuity information of coupler path into account.
However, most of them are defined only for closed loop curves.
Ullah and Kota\cite{ullah1997} have presented an invariant approach towards representation and synthesis of closed loop paths through shape optimization.
They use a combination of global and local search methods for optimizing Fourier Deviant function, to compute the dimensions of planar four-bar linkages without an initial guess.
Wu et al.\cite{wu2011} presented a method based on finite Fourier series for open and closed path generation, but it is specific to four-bar mechanisms.
In the case of motion generation, Li et al.\cite{li2016} have developed a Fourier descriptor-based approach for approximate motion generation.
Bu$\acute{s}$kiewicz et al.\cite{Buskiewicz2009} used curvature of the coupler curve for path synthesis using Genetic Algorithms.
Khan et al.\cite{khan2015} presented on approach where an artificial neural network is used for mapping between Fourier coefficients corresponding to a coupler path and corresponding linkage parameters.
% ---

@@

The above methods generate data based on uniform sampling in the linkage parameter space.
Given highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to a nonuniform sampling of trajectory space, which causes under-representation of possible motions.
We address this issue by employing log-normal distribution in the linkage parameter space to generate the data samples.
Then, we perform compact clustering of the data using machine learning techniques.
A hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in lower levels.
Wandling~\cite{wandling2000} and Yu et al.~\cite{yue-pathgen2011} have built libraries with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
In contrast to this, we need to store only one curve that represents all the segments in it.
This is because our representation facilitates part-to-whole matching.
None of the other previous methods facilitate this partial matching of open motion curve into another open or closed curve, which significantly contributes to providing a large number of solutions, and reduces the data requirement even further.
%  ---
\subsection{The Method Overview}

The original contributions in the paper are as follows:

1) a perceptive problem formulation for path and motion generation, that solves the issues associated with precision point approach.
The formulation is based on a measure of dissimilarity between two planar motions or paths, which is invariant to similarity transforms.
2) we exploit the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering.

%In this paper, we 1) employ pattern recognition and computational shape analysis, to create a similarity transform-independent signature for coupler path and motion, 2) exploit the nonlinear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.

In this paper, we employ pattern recognition and computational shape analysis, to create a similarity transform-independent signature for coupler path and motion.
When a user provides the prescribed motion or path, a query representing invariant signature \footnote{path or motion signature} of the input is raised for $k$ nearest neighbors among cluster centers in the database.
These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task and the coupler motion or path generated by current linkage parameters.
This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect-free throughout the task.
Figure~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.

@@

Here, $p$ acts as a template that tries to find the best match against $W$ while sliding over it along $j$.
Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment\footnote{\emph{Path} is identical to a portion of \emph{Whole}.} of $p$ inside $W$.

@@

\begin{eqnarray}\label{nnlayer}
  h_i = ReLU(W_{i}h_{i-1} + b_{i}), \\
  ReLU(x) = max(0, x),
\end{eqnarray}
where $W_i$ is weight matrix with dimensions $(d^{i}, d^{(i-1)})$ and $b_i$ is $d^{(i)}$ dimensional bias vector of $i^{th}$ layer, which are computed in the process of training.
Auto-encoders are trained to reconstruct the input, in this way each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
The objective of training is to find out the set of weights and biases that minimizes the error loss given by,

@@

Now, when the user raises a query, we use the distance function from sec.~\ref{sec_distanceMetric} for finding $k$ nearest neighbors among $1500$ cluster centers.
If a cluster center is not sufficiently close, we descend into its corresponding cluster to find the closest data point.
Motion with highest similarity score is returned along with its corresponding linkage parameters, which if required, are further fine-tuned to match the query using local optimization methods. Computationally, on a 2.4 GHz Core i5 MacBook Pro with 8 GB memory, every query takes 23 seconds on average to find the sorted list of nearest neighbors among cluster centers.

@@

The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
The motion data is tabulated in Table ~\ref{poseData} to which we fit a B-spline with cord length parametrization in order to get the parametric representation of motion.
The task can also be treated as a finite position motion generation and solved for valid solutions.
We try with our real-time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{shrinathpurwar2017} but obtained solutions suffer from circuit defect, which is not surprising as those methods do not account for the continuity of input positions.
Also, It is obvious that the coupler should not drop the snow during its entire motion except at the end.
The prescribed motion entails this information.
However, precision point approach cannot capture it.

Now we employ the approach presented in this paper.
The first step is to calculate motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
For that, we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
Next, we raise the signature query for nearest signatures among cluster centers of the database.
Fig.~\ref{queryResult} shows nine nearest neighbor signatures along with the task signature.
Table~\ref{ex2_knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
Coupler motions of these linkages have a part, which matches with the shape of input motion query.
Actual scaling and orientation of the linkage can be found out easily by comparing analogous points, which are given by the offset index $j$ that corresponds to minimum distance$(E_{min})$ in Eq.~\req{mccEq}.
Figure~\ref{ex2_solns} depict the solutions obtained after scaling and orienting the linkage to match required motion.
All of these linkages satisfactorily perform the input task without any defect.
As ground or fixed pivot locations should lie above the ground, all solutions except the $4^{th}$ solution are suitable for the task.
Although Fig.~\ref{ex2_solns} shows that $5^{th}$ and $7^{th}$ solution may slightly interfere with the ground, it can be rectified by lifting the mechanism slightly up or making small changes in coupler dimensions.
In light of these results, we can say that this approach produces a large variety of solutions, which otherwise would be very hard to find using precision point approach.

>>>>

The classical mechanism synthesis problem deals with computing type and dimensions of a linkage system for performing specific tasks, which are categorized as the path, motion and function generation.
Path generation task aims to synthesize a mechanism which can guide a point along a prescribed path.
On the other hand, the objective of motion generation task is to synthesize a mechanism which can guide a rigid body along a prescribed motion.
The prescribed path is a time sequence of positions, whereas the prescribed motion is a time sequence of positions and orientations.
For an exhaustive reference, see books from McCarthy and Soh \cite{sohmccarthy}, Sandor and Erdman~\cite{Sandor}, Hunt~\cite{Hunt78}, Hartenberg and Denavit \cite{Hartenberg},  Suh and Radcliffe \cite{Suh78}, and Lohse \cite{lohse2013}.
Various approaches have been proposed in the literature with aim of finding acceptable solutions for path and motion generation problem.
In the majority of the methods, the first step is choosing a mechanism type and then calculating the design parameters of chosen mechanism type.
The first step is called as Type Synthesis, and the later step is called as Dimension Synthesis.
This paper presents an approach to Dimension Synthesis of planar four-bar linkages, but the approach is general enough to be applied on any planar linkage.

\subsection{Motivation}
The majority of mechanism synthesis methods are based on the precision point approach.
This approach is a clever approximation trick to solve the abovementioned tasks, where the task is discretized into precision points.
These points instead of the actual task, are treated as interpolation or approximation task for mechanism synthesis.
However, this way of formulation loses important information about the actual continuous task and can lead to solutions with the order, circuit and branch defects.
The defect in a mechanism renders itself useless for its intended application.
The defects in the single degree of freedom mechanisms are thoroughly discussed by Chase and Mirth\cite{chasemirth}.

Let's see an example of this in a motion generation task.
The objective is to synthesize a four-bar mechanism that can perform the prescribed motion.
Figure~\ref{circuit_defect} shows the prescribed motion and its discretized precision positions.
In the case of motion generation problem, a four-bar can go through at most five precision positions and it is called as classical Burmester~\cite{Burmester86} problem.
For this type of problem, only finite solutions exist and in this case only one solution is obtained as shown in the Fig.~\ref{circuit_defect}.
Although it can be seen that coupler of the four-bar passes exactly through five precision positions, it can not do it without changing the circuit.
A circuit represents an assembly mode in which the mechanism is put together.
This phenomenon is called circuit defect in the linkage, which makes the linkage useless for the prescribed task.
To deal with it, a naive approach is to tweak precision positions in a brute-force way within the tolerance until a solution is found.
Even if the defect-free solution is found, the coupler motion in-between the precision points may go through undesired position and orientation.
This happens because the method discards the functional aspect of continuous motion and turns it into a vacuous interpolation problem.
This tells us that just finding a defect-free linkage with respect to the precision positions is not enough to qualify as a useful mechanism.

Thus, we present a perceptive way of synthesizing defect free linkages for motion and path generation problems.
%As a guiding direction to advance state of the art, we propose following criteria for an effective mechanism synthesis method,
%  \item \textbf{Data Driven}: The method should evolve by learning from its previous experiences, including providing quicker solutions for problems similar to previously solved problems.
%\end{enumerate}
To capture the complete prescribed task, we represent it as a continuous parametric curve.
The objective is to find a linkage, that has a coupler motion or path compatible with the task.
We developed the compatibility measure in a way that is invariant to similarity transformations.
Next step is to conduct a search in the space of linkage parameters to find linkages with coupler motions compatible with the prescribed task.
Although global search methods can be applied for finding solutions, we employ an efficiently clustered database and Powell's local search method to come up with a variety of different solutions.
The motivation behind using clustered database is rooted in the broader objective of machine design.
Mechanism synthesis is a part of the conceptual design phase, which is one of the earliest stages of product design cycle of a machine.
Thus, the synthesis method should be prolific in terms of concept generation to 1) realize the potential of attainable design possibilities, and 2) have the agility to adapt a design to evolving requirements.
The method only deals with the coupler curves and is indifferent to the linkage type.
Thus, it is readily scalable to any type of planar linkage.
In section~\ref{subsec_motiongen}, we present the obtained solutions for the prescribed motion presented in the Fig.~\ref{circuit_defect}.

\subsection{Literature Survey and Overview}
% Global search methods
Instead of brute-force search within tolerance regions, some approaches apply separate constraints to take care of the defects and form an optimization problem of Non-Differentiable objective function.
It can be solved by metaheuristic algorithms like Differential-evolution(DE), Particle Swarm Optimization (PSO), Cuckoo Search (CS).
Cabrera et al.\cite{Cabrera2002} used Genetic Algorithm as the tool for optimization in mechanism synthesis.
Sardashti et al.\cite{sardashti2013} used PSO towards the defect-free synthesis of four-bar linkage with joint clearance for path generation problem.
Ebrahimi and Payvandy\cite{Ebrahimi2015} presented an application of Imperialist Competitive Algorithm (ICA) for synthesizing path generating four-bars having desired workspace limits.
Bulatovic\cite{Bulatovic2013} used Cuckoo Search for solving the problem of optimum synthesis of a six-bar double dwell linkage.
The above methods can produce many defect-free solutions and are scalable to any type of linkages.
However, these methods tend to be slow and inefficient as they start from scratch for every instance with no guarantee of converging to an acceptable solution.

Path synthesis methods based on Fourier analysis do take the continuity information of coupler path into account.
However, most of them are defined only for closed loop curves.
Ullah and Kota\cite{ullah1997} have presented an invariant approach towards representation and synthesis of closed loop paths through shape optimization.
They use a combination of global and local search methods for optimizing Fourier Deviant function to compute the dimensions of planar four-bar linkages without an initial guess.
Wu et al.\cite{wu2011} presented a method based on finite Fourier series for open and closed path generation of four-bar mechanisms.
In the case of motion generation, Li et al.\cite{li2016} have developed a Fourier descriptor-based approach for approximate motion generation.
Bu$\acute{s}$kiewicz et al.\cite{Buskiewicz2009} used curvature of the coupler curve for path synthesis using Genetic Algorithms.
Khan et al.\cite{khan2015} presented on approach where an artificial neural network is used for mapping between Fourier coefficients corresponding to a coupler path and corresponding linkage parameters.
% ---

@@

The above methods generate data based on uniform sampling in the linkage parameter space.
Given highly nonlinear mapping between linkage parameters and coupler trajectory, this way of sampling leads to a nonuniform sampling of trajectory space, which causes under-representation of possible motions.
We address this issue by employing log-normal distribution in the linkage parameter space to generate the data samples.
Then, we perform compact clustering of the data using machine learning techniques.
A hierarchy is created in the database by means of clustering, where the top level comprises of data points called cluster centers, which are representative of the cluster points in lower levels.
Wandling~\cite{wandling2000} and Yu et al.~\cite{yue-pathgen2011} have built libraries with all possible coupler curves, where one curve is broken down into many segments for creating data for partial curves.
In contrast to this, we need to store only one curve that represents all the segments in it.
This is because our representation facilitates part-to-whole matching.
None of the other previous methods facilitate this partial matching of open motion curve into another open or closed curve, which significantly contributes to providing a large number of solutions, and reduces the data requirement even further.
%  ---

The synthesis routine starts by creating a continuous parametric representation of a prescribed path or motion.
we employ pattern recognition and computational shape analysis to create a similarity transform-independent signature for a parametric path and motion.
A query representing invariant signature \footnote{path or motion signature} of the prescribed path or motion is raised for $k$ nearest neighbors among cluster centers in the database.
These $k$ neighbors, if needed, are subjected to fine-tuning by local optimization to obtain a set of defect-free solutions.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task and the coupler motion or path generated by current linkage parameters.
This distance measure of dissimilarity inherently requires continuity of motion, thus ensuring that the output mechanism is defect-free throughout the task.
Figure~\ref{overallMethod} illustrates an overview of our method, which is codified in Algorithm~\ref{alg_overall}.

The original contributions in the paper are as follows:
1) a perceptive problem formulation for path and motion generation, that solves the issues associated with precision point approach,
%The formulation is based on a measure of dissimilarity between two planar motions or paths, which is invariant to similarity transforms.
2) we exploit the nonlinear nature of the relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) an algorithm for partial matching of motions and paths which significantly improves the synthesis of open prescribed tasks.

%In this paper, we 1) employ pattern recognition and computational shape analysis to create a similarity transform-independent signature for coupler path and motion, 2) exploit the nonlinear nature of relationship between the linkage parameters and coupler motions to create a sensitive, wide-ranging, compact, and efficient database with hierarchical clustering, and 3) enable dimensionality reduction using Auto-encoder Neural Networks.

@@

Here, $p$ acts as a template that tries to find the best match against $W$ while sliding over it along $j$.
Domain of $Cn(j, p, W)$ is [0, 1], where 1 represents the complete embedment\footnote{\emph{Part} is identical to a portion of \emph{Whole}.} of $p$ inside $W$.

@@

\begin{eqnarray}\label{nnlayer}
  h_i = ReLU(W_{i}h_{i-1} + b_{i}), \\
  ReLU(x) = max(0, x),
\end{eqnarray}
where $W_i$ is weight matrix with dimensions $(d^{i}, d^{(i-1)})$ and $b_i$ is $d^{(i)}$ dimensional bias vector of $i^{th}$ layer, which are computed in the process of training.
Auto-encoders are trained to reconstruct the input.
In this way each layer encodes the input, which is sufficient for the next layers to reconstruct the output.
The objective of training is to find out the set of weights and biases that minimizes the error loss given by,

@@

Now, when the user raises a query, we use the distance function from sec.~\ref{sec_distanceMetric} for finding $k$ nearest neighbors among $1500$ cluster centers.
If a cluster center is not sufficiently close, we descend into its corresponding cluster to find the closest data point.
Motion with highest similarity score is returned along with its corresponding linkage parameters.
If required, the parameters are fine-tuned to match the query using local optimization methods.
Computationally, on a 2.4 GHz Core i5 MacBook Pro with 8 GB memory, every query takes 23 seconds on average to find the sorted list of nearest neighbors among cluster centers.

@@

The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
The motion data is tabulated in Table ~\ref{poseData} to which we fit a B-spline with cord length parametrization in order to get the parametric representation of motion.
The task can also be treated as a finite position motion generation and solved for valid solutions.
We try with our real-time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{shrinathpurwar2017} but obtained solutions suffer from circuit defect, which is not surprising as those methods do not account for the continuity of input positions.
Also, It is obvious that the coupler should not drop the snow during its entire motion except at the end.
Although, the prescribed motion entails this information, precision point approach cannot capture it.

Now we employ the approach presented in this paper.
The first step is to calculate motion signature of the task motion using steps mentioned in Algorithm ~\ref{alg_signature}.
For that we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
Next, we raise the signature query for nearest signatures among cluster centers of the database.
Fig.~\ref{queryResult} shows nine nearest neighbor signatures along with the task signature.
Table~\ref{ex2_knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
Coupler motions of these linkages have a part, which matches with the shape of input motion query.
Actual scaling and orientation of the linkage can be found out easily by comparing analogous points, which are given by the offset index $j$ that corresponds to minimum distance$(E_{min})$ in Eq.~\req{mccEq}.
Figure~\ref{ex2_solns} depict the solutions obtained after scaling and orienting the linkage to match required motion.
All of these linkages satisfactorily perform the input task without any defect.
As ground or fixed pivot locations should lie above the ground, all solutions except the $4^{th}$ solution are suitable for the task.
Although Fig.~\ref{ex2_solns} shows that $5^{th}$ and $7^{th}$ solution may slightly interfere with the ground, it can be rectified by lifting the mechanism slightly up or making small changes in coupler dimensions.
In light of these results, we can say that this approach produces a large variety of solutions, which otherwise would be very hard to find using precision point approach.
